### 2023-03-30 Documentation/WT group/NHL/Introduction/Introduction.tex
documentation

@@

\section{Project objectives}
\label{sec:objetivos}

@@

\begin{enumerate}[a)]
\item Item 1;
\item Item 2; 
\item Etc.     
\end{enumerate}

@@

\clearpage

>>>>

The biggest motivation to use EHDA is to have a more precise and uniform size and shape of droplets creation.

@@

\section{Project Goals}
\label{sec:objetivos}

@@

multipurpose applications
both scientific and industrial application

\begin{enumerate}[a)]
\item Fully automated and intuitive system for EHDA research and industrial application.
\item Real Time non-visual classification.    
\item Control and stabilization of desired spraying modes.   
\item System Portability.
\end{enumerate}

@@
